### 2018-06-19 doc/latex/02-Software.tex
Latest fixes

Stride is written in C++ and portable over all platforms that have the GNU C++ compiler. 
The following tools needs to be installed:
\begin{compactitem}
    \item g++
    \item make
    \item CMake (\textgreater = v3.10)
    \item Boost
    \item Qt (\textgreater = 5.9, optional, for visualization)
    \item Python (optional, for automatization)
    \item Doxygen (optional, for documentation)
    \item LaTeX (optional, for documentation)
\end{compactitem}

@@

The Application Programmer Interface (API) documentation is generated automatically 
using the Doxygen tool ((see \url{www.doxygen.org}) from documentation instructions 
embedded in the code .

@@

The project directory structure is very systematic.
Everything used to build the software is stored in the directory \texttt{./src}:
\begin{compactitem}
    \item \texttt{src/main}: Code related files (sources, third party libraries and headers, ...)
      	\begin{itemize}
        		\item \texttt{src/main/<language>}: source code, per coding language: cpp (for C++), python, R,   
        		\item \texttt{src/main/resources}: third party resources included in the project: 
        \end{itemize}
    \item \texttt{src/doc}: documentation files (API, manual, ...)
      	\begin{itemize}
        		\item \texttt{src/doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
        		\item \texttt{src/doc/latex\_man}: files needed to generate the user manual with Latex
        \end{itemize}
    \item \texttt{src/test}: test related files (scripts, regression files, ...)
\end{compactitem}

>>>>

Stride is written in C++ and portable over all platforms that have a sufficiently recent version of the GNU C++ compiler. 
The following tools needs to be installed:
\begin{compactitem}
    \item g++
    \item make
    \item CMake (\textgreater = v3.10)
    \item Boost (\textgreater = 1.66 is known to work)
    \item Qt (\textgreater = 5.9, optional, for visualization)
    \item Python (optional, for automatization)
    \item Doxygen (optional, for documentation)
    \item LaTeX (optional, for documentation)
\end{compactitem}

@@

The Application Programmer Interface (API) documentation is generated automatically 
using the Doxygen tool (see \url{www.doxygen.org}) from documentation instructions 
embedded in the code .

@@

The project directory structure is very systematic.
Everything used to build the software is stored in the root directory:
\begin{compactitem}
    \item \texttt{main}: Code related files (sources, third party libraries and headers, ...)
      	\begin{itemize}
        		\item \texttt{main/<language>}: source code, per coding language: cpp (for C++), python, R,   
        		\item \texttt{main/resources}: third party resources included in the project: 
        \end{itemize}
    \item \texttt{doc}: documentation files (API, manual, ...)
      	\begin{itemize}
        		\item \texttt{doc/doxygen\_ref\_man}: files needed to generate the reference documentation with Doxygen
        		\item \texttt{doc/latex\_man}: files needed to generate the user manual with Latex
        \end{itemize}
    \item \texttt{test}: test related files (scripts, regression files, ...)
\end{compactitem}
